Rough Draft

### 2017-09-30 literature reviews/roughdraft.tex
edited materials, methods, results sections

%-----------------------------------------------------------------------------------
\title{Literature Review of Online Question Forums}
\author{Lisa Oshita}
\date{}
%-----------------------------------------------------------------------------------

@@

    Community-driven online question and answer forums (CQA) are becoming widley used sources of information. These online platforms allow for anyone to ask or answer a question. It provides a place for people of all backgrounds and levels of expertise to provide input on a certain question. One popular CQA is Yahoo! Answers. This platform features questions of all topics, from politics, to food and drink, and even mathematics. On the other hand of the spectrum is Stack Overflow, the CQA that features strictly computer programming question and answers. This forum reiceves around 40 million visits every month. This platforms ultimately provide people with a place to share their knowlege, and clearly are becoming increasingly popular sources of information.

    The CQA discussed in this paper is iFixit's Answers forum. iFixit is a company founded in 2003 by two engineering students of the California Polytechnic State University in San Luis Obispo. What began as a small business running out of the college dorms, is now a company that helps thousands of people fix their broken devices everyday, providing over 30,000 free repair guides with pictures and step-by-step instructions. iFixit also sells the specialized tools and parts used in their repair guides, specialized tools like an iPhone 7 batter adhesive strip or a Nexus 9 LCD screen and digitizer. The main goal of this company is to teach people how to fix their own devices, and in extending the lifetime of their own devices, they save money and cut down on electronic waste. As such, this company helps thousands of people fix their devices everyday.

@@

    Suggestions for how users can ask questions to minimize answer times, as well as suggestions for how the forum design can be improved, can be derived from such analysis. However, to the best of our knowledge, analysis and prediction of answer times on forums has not been investigated by many researchers. A majority of the research focuses on assessing and predicting the question and answer quality. As such, there is need for further analysis of response times in these forums. This paper presents a survival analysis on the time until a question is answered on iFixit's Answers forum. It attempts to determine the factors that are significantly related to answer time, and create a cox proportional hazards model that can accurately predict the survival probability of a question.

@@

    In regards to investigation of forum response times, \citep{Bhat2014} developed a classification model (? is that what it's called) to analyze response times of questions posted on Stack Overflow, and found that tag-based features like the number of tags included or the number of subscribers a certain tag has, were the best predictors of answer time.

@@

\section{Materials and Methods}

    The data set analyzed in this paper contained 7,760 questions posted from April 8, 2017 to July 7, 2017. 63.8\% of the questions recieved an answer before the data was downloaded. The distribution of answer times is highly right skewed, shown in figure a. The mean answer time was 355.93 hours, or 14.83 days, and the median answer time is 8.79 hours. These values factor in questions that did not recieve an answer. Within an hour, 26.59\% of the questions received an answer. After one day, 57.35\% of questions recieved an answer. Variables within the data set included information about the questions, like the title, the body text, device, date it was posted, and information about the user like whether or not the user was considered new (or a member for less than 24 hours) at the time the question was posted.

    Variables created in the model:

The time until event variable used in the cox regression model is defined as the time until a question receives its first answer. If a question received an answer, this was calculated as the time from the date the question was posted to the date the first answer was received. If the question did not receive an answer, this was calculated as the time from the date the question was posted, to the date the date set was downloaded. The censoring variable needed in a cox regression model, is 0 if the question remained unanswered by the time the data set was downloaded, and 1 if the question received an answer.

Newcategory

This variable categorized the devices of the questions based off of the existing category variable as well as several other factors. The original category variable had NAs, which were a result of the asker creating a question for a device not already featured on the website, and were coded to “Other”. All Apple products (e.g., iPhones, iMacs, Apple watches) were given their own category. After pulling out iPhones from the original “Phones” category, the remaining phones were categorized as “Android/Other Phone”. Appliance and Household categories of the original variable were merged into “Home”. “Car and Truck” were added to the “Vehicle”. Lastly, any category that contained less than 2% of the questions were categorized as “Other”.

Containanswered and contain_unanswered were created based off of the idea that certain key words would be more likely to catch an user’s eye, and would make them get answered more quickly. This was also based on the idea that certain words might also not be as popular, and would be common amongst questions that remained unanswered. As such, contain_answered and contain_unanswered are logical variables indicating true if a question’s title contains a term that is considered frequently used among answered or unanswered questions, respectively. To create these variables, the data set was separated between answered and unanswered questions. For each set, the occurrence of each word in every title was summed to get the frequencies of each word. Thus, we had a two lists of words—one consisting of the words within answered questions’ titles and their frequencies, and the other consisting of the words within unanswered questions’ titles and their frequencies. From these two lists, rules were applied to determine if a word can be considered “frequently used”.  For frequently used words in answered questions, that word would have to appear in more than 1percent of the titles, and would have to have a ratio of greater than 1. For a word to be considered “frequently used” among unanswered questions, that word would have to appear in more than 1percent of the question, and would have to have a ratio of less th san 1. Thus, we ended up with two sets of words, one set contained the most frequently used words in answered questions, and the other set contained the most freuqnelty used words in unanswered questions. Since there was some overlap between the words and the devices and category levels, any words that matched with a category were removed. That resulted in lists of 111 words for answered questions, and 32 words for unanswered questions. Contain_answered indicated true if a question’s title contained at least one of the words from the frequently used words among the answered questions. Contain_unanswered indicated true if a questions title contained at least one of the words from the frequently used words among the answered questions.

Title_questionmark and title_beginwh 
These two variables were created to determine if stating the title in the form of a question is associated with faster answer times. Title_questionmark is a logical variable indicating true if the question ends in a question mark. Title_beginwh is a logical variable indicating true if the title begins with a “wh” word, like “what” or “when”. These variables were taken from mined your own tags

Text_contain_punct.
This is a logical variable indicating true if the question’s text contains any end punctuation marks (. ? !). This variable was created to investigate if run-on sentences (sentences with no end punctuation marks) take longer to receive an answer.

Text_all_lower
This is a logical variable indicating true if the text of the question is in all lower case.

Update 
This is a logical variable indicating true if the asker updated the question (edited or added information about the question) after posting it.

Greeting
Logical variable indicating true if the asker included a greeting (e.g. “Hello”, “Hi”) as the first word of the text
Gratitude
Logical variable indicating true if the asker used manners in the question of the text (e.g. “Thank you”, “please”, “appreciate”)

Prior_effort 
Logical variable indicating true if the asker used language that indicates that prior effort or research was done before asking the question. (e.g. “tried”, “attempted”, “tested”). This variable was inspired by

Weekday 
The day of the week the question was posted

Ampm 
The time of day the question was posted. If the question was posted between 5am and 12pm, it was categorieze das morning. If it was posted between 12pm and 5pm, it was categorized as afternoon, between 5pm and 8am- “evening”, and 8pm and 5 am, “night”

Avg_tag_score
The frequency or “score” of a tag is defined as the proportion of times that tag appears in the data set. This variable is the average of all of a question’s tag “scores” or frequencies. This variable was created to investigate if questions that include popular tags, or tags that are used frequently, have faster answer times. This variable was inspired by

Text_length
The number of characters in the text

Device_length
The number of characters in the user-defined device variable. This variable was included to capture when a user incorrectly inputs their device. For example, question 390271 includes a device that is 136 characters long--“Turtle Beach Ear Force Xmy grandson chewed through the wire while we was playing it's brand-new is there anyway I can have it fixedO One”. 11 questions also didn’t include any device name. this variable was created to capture these user errors

Avg_tag_length
The average number of characters in the user-defined tags. This variable, like the device-length variable, was created to capture when a user incorrectly used the tagging system. An example of an incorrect tag is question 390989 and says: “i need to repair the headset because i can not find the bluetoot” and comes ot 64 charahcters. If a question did not include a tag, this variable was set to 0.

Newline_ratio
This variable is calculated as the ratio of the number of newlines a question includes, over the number of characters in the questions text. This variable was included on the assumption that questions with text that is more readable get faster answer times. Questions with long text and also include newlines are generally easier to read than questions that don’t include any newlines.

Variables included in the final model

The above variables were all entered into the final model. The final model was stratified on ampm, as prior analysis indicated that this variable violated the proproitnal hazard assumption. The square root of the avg_tag_score was entered. Viewing the plot of answer times against the avg_tag_screo variable indicated heavy skewing. Taking the square root of this variable helped pull in the larger values. The quadratic term was included for text_length. This was included, since it was hypothesized that texts that were either too short or too long would have higher answer times. In other words, there might be a sweet spot on the text_lenght. Restricted cubic splines were included for device_length, avg_tag_length, and newline_ratio. The method for fitting these variables was taken from frank harrels text book. These variables were fit as restricted cubic splines with 5 knots initially. The final includes 5, 4, and 4 knots, as this model with this number of knots had the lowest Aic.

Methods

Univariate analysis for each of the variables of interest was carried out on one of the training data sets. Variables with a p-value of less than 0.01 were entered into the final model. Since this is a predictive model, it was decided that all variables would be kept in the model, to maintain predictive power. After building the model on one of the training data sets, assumptions and residuals were checked.

Initally, ampm was put in the model without any stratification. Checking the proportional hazards assumption, by both examinging the schoenfeld residuals as well as the cox.zph function in r, indicated that ampm violated the proportional hazard assumption. It was decided that this variable would be stratified on.

Checking the plot of martingale residuals shows that there doesn’t appear to be any obvious pattern, indicating that the functional form seems adequate (how to check residuals for splines??)

Checking the deviance residuals shows that a considerable amount of questions have residuals with an absolute value of well over 2.5. Taking those questions out of the data set and refitting the model and performing cross validation, showed that fitting the model without these questions resulted in worse predictive performance.

Looking at the score resiudals for each predictor indicated that there may be a couple points that can be considered influential. Experimentation with those questions, and refitting the model without those certain points, along with performing cross validation, showed that refitting the model without those question resulted in worse predictive performance, similar to how it did for the deivcance resiudals. 
After determining that the model did not grossly violate any assumptions or have any weird residuals, a cross-validation scheme was carried out.

A cross-validation scheme was used for this analysis. The data set was split into 5 training and test data sets. Training data sets had 6,208 questions and test data sets had 1,552 questions. The model was built on the training data sets, and tested on the corresponding test data sets. To assess the prediction performance of this model, metrics similar to /cite{Chen} were computed. The model and it’s coefficients, built on the training data sets, were then use to calculate the predicted hazard ratios for questions in the test data sets. Those predicted hazard ratios were then entered into another cox regression model with the time until answer as the survival time variable. Metrics calculated were the hazard ratio for this model, along with the partial loglikelihood score and respective p-value. The AIC and R-square was also evaluated (explain what this is in survival analysis). Somers Dxy along with a concordance statistic were also calculated as performance metrics. This process was repeated each time a model built on a training data set was fit and predicted on the test data set. The metrics taken into consideration was the average of all of the metrics computed on the test data sets. The same metrics were also computed for predictions on the training data set itself. Although the metrics were not considerably high or impressive, they did not change from training data set to test data set.

Lastly, the model was fit to the full data set. The same process and metrics were calculated. Metrics for the full data set are not different from the results of our cross validation plan.

Results and Discussion (or separate the two).

The final model gave an AIC value of 69945.32. The partial loglikelihood ratio test statistic was 1307.15 with a p-value of 0. The R-squared value for this model is 0.1555. Variables that proved to be significant predictors with a p-value of less than 0.01 are: new_category (apple product, camera, game console, home, pc, and vehical), contain_unanswered, title_quesitonmark, update, prior_effort, avg_tag_score and the spline on avg_tag_length.

@@

>>>>

%-----------------------------------------------------------------------------------
\title{Rough Draft}
\author{Lisa Oshita}
\date{}
%-----------------------------------------------------------------------------------

@@

    Community-driven online question and answer forums (CQA) are becoming widley used sources of information. These online platforms allow for anyone to ask or answer a question. It provides a place for people of all backgrounds and levels of expertise to provide input on a certain question. One popular CQA is Yahoo! Answers, featuring questions of all topics and expertise levels. On the other hand of the spectrum is Stack Overflow, the CQA that features strictly computer programming question and answers. Forums liek these 2 recieve around 40 million visits every month. These online question and answer forums are clearnly becoming popular sources of information.

    The CQA analyzed in this paper is iFixit's Answers forum. iFixit is a company founded in 2003 by two engineering students of the California Polytechnic State University in San Luis Obispo. What began as a small business running out of the college dorms, is now a company that helps thousands of people fix their broken devices everyday, providing over 30,000 free repair guides with pictures and step-by-step instructions. iFixit also sells the specialized tools and parts used in their repair guides, specialized tools like an iPhone 7 batter adhesive strip or a Nexus 9 LCD screen and digitizer. The main goal of this company is to teach people how to fix their own devices, and in extending the lifetime of their own devices, they save money and cut down on electronic waste. As such, this company helps thousands of people fix their devices everyday.

@@

    Suggestions for how users can ask questions to minimize answer times and for how the forum design can be improved, can be derived from such analysis. However, to the best of our knowledge, analysis and prediction of answer times on forums has not been investigated by many researchers. A majority of the research focuses on assessing and predicting the question and answer quality. As such, there is need for further analysis of response times in these forums. This paper presents a survival analysis on the time until a question is answered on iFixit's Answers forum. It attempts to determine the factors that are significantly related to answer time, and create a cox proportional hazards model that can accurately predict the survival probability of a question.

@@

    In regards to investigation of forum response times, \citep{Bhat2014} developed a classification model to analyze response times of questions posted on Stack Overflow, and found that tag-based features like the number of tags included or the number of subscribers a certain tag has, were the best predictors of answer time.

@@

\section{Materials}

    The data analyzed in this paper contained 7,760 questions posted from April 8, 2017 to July 7, 2017. We worked exclusively with questions in English. Of the questions in the data set, 4,951, or 63.8\%, recieved an answer before the data was downloaded. Questions that remained unanswered were considered right-censored. The time until event variable used in survival analysis methods was defined as the time until a question posted on the forum recieves an answer. Comments posted on the question are not considered answers, and an answer does not have to be accepted as the ``chosen solution'' to be considered the answer. We are only considering the time until the question recieves its first answer. The time until answer value for right-censored questions, questions that did not recieve an answer, is defined as the time from when the question was posted, to the time the data was downloaded. Figure a shows the distribution of answer times for all questions in the data set.

    The following statistics were calculated from Kaplan-Meier estimates of survival probabilities for each question in the data. As Kaplan-Meier estimates adjust for the presence of censored observations, these statistics are adjusted for the presence of unanswered questions. In this analysis, survival is defined as the event that a question remains unanswered beyond a certain time, t. For questions in this data set, the mean survival time, or the average time until a question recieves its first answer is 775.75 hours, or 32.32 days. The median survival time, the time at which 50\% of the questions in the data recieved an answer is 9.16 hours. Table 1 provides more percentiles of survival time. 
    Figure A shows the Kaplan-Meier Curve for all questions in the data. The curve indicates that around 100 hours, the probability that a question recieves an answer after that time hovers around 0.35. The survival probability never reaches 0 due to the large amount of unanswered questions.

    Variables created:

    The data contained information about each question's title, text, and device, from which we created the following variables to use in the cox regression model.

The time until a question recieves its first answer, as described above, was calculated as the time from the time the question was posted to the time the first answer was received in hours. If the question did not receive an answer, the time until answer value was calculated as the time from when the question was posted, to the time the data was downloaded, July 7, 2017 at 2:41 PM PDT. The censoring variable indicates 1 if the question received an answer, and 0 if the question remained unanswered by the time the data set was downloaded.

Categorical Variables:

Questions were categorized based off of the devices it pertains to. Categories include: Apple Products, Android\/Other Phone, PC, Tablet, Electronics, Camera, Vehicle, Game Console, Home, Other. Home, Vehicle, Other. Table B shows the percentage of questions within each device category.

Whether or not the question's title contains at least one word that is considered ``frequently used'' among answered questions.

Whether or not the question's title contains at least one word that is considered ``frequently used'' among unanswered question.

Whether or not the question's title ends in a question mark.

Whether or not the question's title begins with a "Wh" word (e.g. "What", "Where").

Whether or not the question's text contains any end punctuation marks (. ? !).

Whether or not the question's text is in all lower case.

Whether or not the asker updated the question's text (e.g., edited or added information) sometime after posting it.

Whether or not the asker included a greeting (e.g. ``Hello'', ``Greetings'') in the question's text.

Whether or not the asker used polite language in the question's text (e.g., ``Thank you'', ``please'').

Whether or not the asker made an effort to solve the problem on their own, prior to asking the question.

The day of the week the question was posted.

The time of day the question was posted. Times include: Morning, Afternoon, Evening, and Night.

Numeric Variables:

The average frequency, or proportion of times a tag appeared in all of the data, for all of a question's user-defined tags. Questions without tags were assigned a value of 0 for this variable.

The average number of characters in each question's tags.

The number of characters in the question's text.

The number of characters in the user-defined device name.

The ratio of the number of newlines to the number of characters in the question's text.

\section{Methods}

Univariate analyses for each variable of interest were performed on one of the training data sets. Variables with a p-value of less than 0.01 were entered into the final model. As the goal of this model is prediction, it was decided that all variables would be kept in the model to maintain predictive power.

5-fold cross-validation was used to assess predictive performance metrics. Each training data set contained 6,208 questions. Test data sets contained 1,552 questions.

For each iteration of cross-validation, the model fit to the training data was used to calculate predicted hazard ratios from the corresponding test data. To assess prediction performance, those predicted ratios were entered into a separate cox regression model as the explanatory variable with the question's answer times as the survival time value. The resulting hazard ratio, R-square statistic, partial loglikelihood and p-value, Somers' Dxy and Concordance statistic for that model were used as indicators of the prediction model's performance. If the performance assessing model gave a significant results, this would indicate that the predicted hazard ratio is signficantly associated with survival time, and that our prediction model performs well. Somers' Dxy and Concordance statistics are measures of how well the model can rank predictions. (add to this) The concept behind these metrics came from \cite{Chen}. These metrics were also computed for predictions on the training data itself. For each iteration, there was no signficant difference between the metrics computed on the training data predictions, and the metrics computed on the test data. Table C shows average metrics for training and test data predictions. The metrics taken into consideration was the average of all metrics computed on test data. Although these metrics are not considerably high, they do not vary signicantly from training to test data sets.

\section{Results and Discussion}

The final model, including all variables described above, was fit to the full data set.
The proportional hazards assumption was assessed by using the cox.zph function of the survival package in R. This test is based on the correlation between scaled Schoenfeld residuals and a function of time. Signficant p-values of this test indicate a possible violation of the proportional hazard assumption. For our model, the "Apple Product" level of the device category variable had the lowest p-value of 0.01. The next lowest p-values hovered around 0.04, for variables like device_length, and the Camera and Game Console levels of category. As Apple Product was the only major violation of this assumption, and stratifying on this variable substantially decreased the predictive power, this assumption was considered to be fine (rewrite this).

Assessing the martingale residuals for each quantitative predictor indicated that the functional form appears to be adequate.

Assessing the deviance residuals shows that a considerable amount of questions have residuals with an absolute value of well over 2.5. However, removing those questions from the data set and and refitting the model with cross-validation techniques resulted in worse predictive accuracy.

Assessing the score residuals for each predictor indicated that some questions might a strong influence on the fit of the model. However, similar to the case with the deviance residuals, refitting the model without those certain questions with cross-validation techniques resulted in worse predictive performance.

The final model included all variables described above, along with the following transformations:

Stratification on the time of day the question was posted.

Square root of the average frequency of a question's tags.

Quadratic polynomial on the length of the question's text.

Restricted cubic splines on the number of characters in the device name, the average length of a question's tags, and the ratio of newlines to number of characters in a question's text. Knots assigned to these variables were 5, 4, 4, respectively.

The final model gave an AIC value of 69945.32. The partial loglikelihood ratio test statistic was 1307.15 with a p-value of 0. The R-squared value for this model is 0.1555. Variables that proved to be significant predictors with a p-value of less than 0.01 are: new_category (apple product, camera, game console, home, pc, and vehical), contain_unanswered, title_quesitonmark, update, prior_effort, avg_tag_score and the spline on avg_tag_length. Include some interpretations of the hazard ratio?

@@

The variables described above were entered into the final cox regression model with these variable transformation

Stratification on ampm: prior analysis of initial cox regression models indicated that this variable violated the proportional hazard assumption. Stratification resolved this violation.

Square root of avg\_tag\_score: Viewing the distribution of answer times against the original avg\_tag\_score variable indicated heavy right skewing. Taking the square root of this variable decreases some of this skewing.

Quadratic polynomial on text_length

Restricted cubic splines were included for device_length, avg_tag_length, and newline_ratio. The method for fitting these variables was applied from \citep{Harrell2015}. Initially, these variables were fit as restricted cubic splines with 5 knots. The model with the lowest AIC included 5, 4, and 4 knots for device_length, avg_tag_length and newline_ratio, respectively. As such, this was the final form for these quantitative variables.

\section{Appendix}

device

The data contained the original category variable as defined by iFixit. This category variable contained NAs (how many), a result of the asker creating a question for a device not already in the website's data base. These missing values were coded to ``Other'' in the new categorization variable. All Apple products (e.g., iPhones, iMacs, Apple watches) were given their own category. After pulling out iPhones from the original ``Phones'' category, the remaining phones were categorized as ``AndroidOther Phone''. Appliance and Household categories of the original variable were merged into ``Home''. ``Car and Truck'' were added to the ``Vehicle''. Lastly, any category that contained less than 2\% of the questions were categorized as ``Other''. All other categories remained the same as the original category. The final categories in the new categorization variable were Apple Product, Android/Other Phone, PC, Tablet, Electronics, Camera, Vehicle, Game Console, Home, and Other.

contain answered and unanswered

  These variables were created based on the intuition that certain topics might be more popular among the answering community, and that questions concerning these topics might recieve an answer faster than questions that don't. It was also based on the flip side of this idea, that certain topics might not be popular, or that some topics might be too narrow or specific and would be common among questions with long answer times or those that remained unanswered. To investigate this intuition, contain_answered and contain_unanswered were created.

  To create these variables, the data was separated between answered and unanswered questions. Using text mining techniques, two lists were created-one for answered questions and another for unanswered questions. These lists contained every word within the question's titles and the frequency, or number of times they occured in their respective data set. For each of these lists, rules were applied to determine if a word could be considered ``frequently use''. For frequently used words in answered questions, that word would have to appear in more than 1\% of the titles, and would have to appear in answered questions more than it appeared in unanswered questions. To determine the latter part, a ratio of proportions was calculated. This ratio was calculated as the proportion of times a word occured among answered questions, to the proportion of times a word occured in unanswered questions. As an example, if ``cracked'' appeared in 2\% of answered questions and in 0.1\% of unanswered questions, it would be considered frequently used among answered questions as it occurs in more than 1\% of answered question's titles and occurs 20 times more in answered questions and in unanswered questions (ratio = 0.02/0.001 = 20). As for unanswered questions, to be considered ``frequently'' used, they must occur in 1\% or more of the question's titles and occur in more unanswered questions than unanswered questions (ratio < 1). Since there was some overlap between the words in each list and the device categories, every word that matched a device name was removed from the list. The resulting list for answered questions was 111 words, and 32 words in uanswered questions. Contain_answered and contain_unasnwered are logical variables, indicating true if a question's title contained at least one of the words in the frequently used words list for answered and unanswered questions, repsectively.

  Title\_questionmark and title\_beginwh

These two variables were created to determine if stating the title in the form of a question is associated with faster answer times. Title_questionmark is a logical variable indicating true if the question's title ends with a question mark. Title_beginwh is a logical variable indicating true if the title begins with a “wh” word (e.g. "what", "when"). These variables were created based off of the findings from \citep{Bhat2014}.

  Text\_contain\_punct

A logical variable indicating true if the question’s text contains any end punctuation marks (. ? !). This variable was created to investigate the intuition that run-on sentences, or sentences with no end punctuation marks, may take longer to receive an answer.

Text\_all\_lower

A logical variable indicating true if the text of the question is in all lower case.

Prior\_effort

Logical variable indicating true if the asker used words that indicate prior effort or research was done before asking the question (e.g. ``tried'', ``attempted'', ``tested''). This variable was created based off of findings from \cite{Bhat2014}.

Ampm (change name)

The time of day the question was posted. If the question was posted between 5am and 12pm, it was categorized as ``morning''. If it was posted between 12pm and 5pm, it was categorized as ``afternoon'', between 5pm and 8am- ``evening'', and 8pm and 5 am, ``night''

Avg\_tag\_score

The frequency or “score” of a tag is defined as the proportion of times that tag appears in the entire data set. Avg\_tag\_score is the average of all of a question’s tag “scores” or frequencies. This variable was created to investigate if questions that include popular tags, or tags that are frequently used and thus have a high "score", also have faster answer times. This variable was created based off of findings from \cite{Bhat2014}.

Avg\_tag\_length

The average number of characters in each question's user-defined tags. If a question did not include a tag, this variable was set to 0. This variable, like the device-length variable, was created to capture when a user correctly or incorrectly used the tagging system. For example, question 390989 includes tag: “i need to repair the headset because i can not find the bluetoot” and is 64 characters long, while question 410254 includes tags "sound", "sound driver" and "speaker" and has an average tag length of 8 characters. It's hypothesized that users who use the tagging system correctly, as in the latter example, recieve answers quicker than the user in the former.

Device\_length

The number of characters in the user-defined device variable. This variable was included to capture when a user incorrectly inputs the device name. For example, the device variable for question 390271 is, “Turtle Beach Ear Force Xmy grandson chewed through the wire while we was playing it's brand-new is there anyway I can have it fixedO One” and is 136 characters long. 11 questions in this data set also didn’t include any device. This variable was created based on the intuition that users who incorrectly define their devices make it harder for answerers to discern the topic of their question, and thus have longer answer times or might not recieve an answer.

Newline\_ratio

This ratio of the number of newlines to the number of characters in the question's text. This variable was based on the intuition that question's that include newlines in the text, are easier to read and thus have faster answer times. long text and also include newlines are generally easier to read than questions that don’t include any newlines.
